\documentclass[10pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{black}
\nopagenumbers{}
\usepackage[utf8]{inputenc}
\usepackage{ragged2e}
\usepackage[scale=0.920]{geometry}
\usepackage{import}
\usepackage{multicol}
\usepackage{import}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{fontawesome5}

\name{Eric}{Scherpereel\linebreak}



\newcommand*{\customcventry}[7][.13em]{
\begin{tabular}{@{}l}
{\bfseries #4} \
{\itshape #3}
\end{tabular}
\hfill
\begin{tabular}{l@{}}
{\bfseries #5} \
{\itshape #2}
\end{tabular}
\ifx&#7&%
\else
{%
\begin{minipage}{\maincolumnwidth}%
\raggedright
#7%
\end{minipage}%
}%
\fi
\par\addvspace{#1}}


\begin{document}
\makecvtitle



\fontsize{10.55}{12.6}\selectfont
\vspace*{-12mm}

\begin{center}
\begin{tabular}{ c c c }
\faMobile\enspace +1 (437) 388-6483 \quad \quad &
\faEnvelope\enspace ericscherpereelarce@gmail.com \quad \quad &
\faHome\enspace Montreal, QC \\

\multicolumn{3}{c}{%
\faGlobe\enspace \href{https://ericscherpereel.netlify.app/}{\textcolor{blue}{Website}}
\quad \quad
\faLinkedin\enspace \href{https://www.linkedin.com/in/eric-scherpereel-arce-191422327/}{\textcolor{blue}{LinkedIn}}
} \\
\end{tabular}
\end{center}




\section{Education}


\customcventry{Expected Graduation: Aug 2028}{{\color{blue}\href{https://www.concordia.ca/}{Concordia University}}}{BCompSc, Computer Science}{Montreal, QC}{}{
{Relevant courses: Data Structures \& Algorithms, Web Programming, Databases, Java OOP\linebreak}}

% \customcventry{2017 - 2024}
% {\color{blue}\href{https://www.escuelaeuropea.org/en/}{European School of Alicante (EEA)}}{European Baccalaureate}{Alicante, Spain}{}{
% {GPA: 4.0/4.0 | Python Competitive Programming Club | Website Maintenance (Pupils’ Committee)\linebreak}}




\section{Experience}

% \customcventry{Oct 2025 -- Present}{{\color{blue}\href{}{CV Maxer}}}
% {Founder \& Software Engineer,}
% {Montreal, QC}{}{
% \renewcommand{\labelitemi}{\textbullet}
% \begin{itemize} \itemsep -2pt
%     \item Built and shipped an AI-powered CV reviewer that parses resumes (\textbf{PDF} \& text) into structured sections and generates ATS-focused scoring + prioritized rewrite suggestions for target roles.
%     \item Implemented job-posting-aware tailoring: extracts required skills/keywords, computes match gaps, and generates role-specific bullet rewrites + cover letters with versioning and side-by-side comparisons.
%     \item Delivered a production full-stack SaaS with \textbf{React/Next.js} + \textbf{TypeScript} and a \textbf{PostgreSQL} backend, including authentication, background jobs for analysis/export, and usage-based billing (credits/subscription) to control LLM API costs. \linebreak
% \end{itemize}
% }



\customcventry{Oct 2025 -- Present}{{\color{blue}\href{}{CV Maxer}}}
{Founder \& Software Engineer}
{Montreal, QC}{}{
\renewcommand{\labelitemi}{\textbullet}
\begin{itemize} \itemsep -1pt
    \item Built a production AI SaaS using \textbf{Next.js, TypeScript, and PostgreSQL}, featuring a custom LLM pipeline that parses complex PDF schemas into structured ATS data with 98\%+ integrity.
    \item Developed a robust cost-governance module to manage \textbf{GPT-4o/mini} expenditures, implementing sub-cent precision tracking and environment-driven daily spend limits for operational sustainability.
    \item Optimized system responsiveness by offloading intensive analysis and PDF generation to asynchronous background jobs, enabling real-time semantic gap analysis and role-specific content tailoring. \linebreak
\end{itemize}
}




\customcventry{Summer 2025}{{\color{blue}\href{https://webgenweb.netlify.app/}{Freelance}}}{Freelance Web Developer,}{Remote}{}{
\renewcommand{\labelitemi}{\textbullet}
\begin{itemize} \itemsep -2pt
  \item Built and launched responsive websites using \textbf{HTML}, \textbf{CSS}, and \textbf{JavaScript}, focusing on performance and mobile UX.
  \item Collaborated closely with clients to implement provided UX designs, translating them into functional interfaces.
  \item Increase new customer acquisition by \textbf{20\%} after launch by improving their web presence.
 \linebreak
\end{itemize}
}







% \customcventry{Dec 2025 -- Present}{{\color{blue}\href{https://students.ieee.org/student-branches/}{IEEE Student Branch}}}
% {Computer Vision Developer,}
% {Montreal, QC}{}{
% \renewcommand{\labelitemi}{\textbullet}
% \begin{itemize} \itemsep -2pt
%     \item Developing a \textbf{Computer Vision} system for an autonomous chess robot to reconstruct the board state from camera input under real-world conditions.
%     \item Designing and implemented an image-processing pipeline in \textbf{Python} using \textbf{OpenCV} and \textbf{NumPy} to detect board geometry, correct perspective distortion, and localize individual squares.
%     \item Applied contour analysis and geometric filtering techniques, collaborating with robotics and control teams to integrate vision outputs into downstream decision-making. \linebreak
% \end{itemize}
% }




\customcventry{Sep 2024 ‐ May 2025}{{\color{blue}\href{https://gdg.community.dev/}{Google Developer Student Club (GDSC)}}}{Software Developer,}{Montreal, QC}{}{
\renewcommand{\labelitemi}{\textbullet} % Makes bullet points black
\begin{itemize} \itemsep -2pt % Reduces space between items
    \item Developing a calendar-based AI web app that predicts and schedules assignment completion times for students using AI.
    \item Gaining hands-on experience in Full Stack Development (JavaScript, TypeScript, React, Node.js, APIs) while collaborating in a team-based project.
    \item Mentored by GDSC leads while contributing to a 5-person agile team, gaining practical experience in AI integration and cloud technologies.\linebreak
\end{itemize}
}



\section{Projects}

\customcventry{2026}{{\color{blue}\href{}{(GitHub)}}}{Moogle Maps,}{}{}{
\renewcommand{\labelitemi}{\textbullet} % Makes bullet points black
\begin{itemize} \itemsep -2pt % Reduces space between items
    \item Built a full-stack mapping platform with \textbf{React, TypeScript, Leaflet, Python, and FastAPI}, featuring a search-first interface, live map overlays, and route cards for walking, biking, bike-share, bus, and metro options.
    \item Created a backend that connects to geocoding, weather, routing, and public-transit feeds, normalizes responses with \textbf{Pydantic}, and exposes clean REST endpoints for the frontend.
    \item Implemented route ranking and demand forecasting using \textbf{Dijkstra-style graph search}, OSRM route geometry, GTFS schedule/shape parsing, \textbf{PostgreSQL}/CSV station snapshots, and ML models to predict station availability. \linebreak
\end{itemize}
}

% \customcventry{McHacks 2025}{{\color{blue}\href{https://github.com/CatosCrack/TrustMP}{(GitHub)}}}{TrustMP,}{}{}{
% \renewcommand{\labelitemi}{\textbullet} % Makes bullet points black
% \begin{itemize} \itemsep -2pt % Reduces space between items
%     \item Developed a web platform that allows users to track MPs' voting records and interact with AI-generated bill summaries and chatbots.
%     \item Built a backend to process parliamentary data using \textbf{Google Cloud}, and \textbf{Gemini API} for summarizing and classifying.
%     \item Implemented a bill-based AI chatbot, enabling users to ask questions about proposed laws without reading the documents. \linebreak
% \end{itemize}
% }


\customcventry{McHacks 2026}{{\color{blue}\href{https://github.com/ericmapple/ATC-Risk-Tool-}{(GitHub)}}}{ATC Risk Tool,}{}{}{
\renewcommand{\labelitemi}{\textbullet}
\begin{itemize} \itemsep -2pt
  \item Built a real-time air-traffic map with \textbf{React + TypeScript} and \textbf{Leaflet}, with track projection + aircraft inspection.
  \item Implemented a \textbf{CPA-based} risk/alert pipeline enforcing 5 NM / 1000 ft minima with severity-ranked filtering (vertical-rate/wake/congestion heuristics).
  \item Integrated \textbf{GeoMet WMS} weather overlays and a \textbf{Gemini} “Explain Alert” UI for concise risk summaries and recommended next checks. \linebreak
\end{itemize}
}




\section{Skills and Area of Expertise}
\begin{description}[leftmargin=0cm, style=unboxed]

    \item[\textbf{Programming Skills:}] Java, JavaScript/TypeScript, Python, C\#, C
    \vspace{-1.5mm}
    \item[\textbf{Other:}] React.js, React Native, HTML, CSS, Node.js, SQL, PostgreSQL, Git
    \vspace{-1.5mm}
    \item[\textbf{Leadership and Software Engineering:}] Project Management, Full-Stack Development, System Architecture, Hackathons \& Rapid Prototyping, Prompt Engineering, Software Engineering Practices
\end{description}





\section{Languages}
\begin{minipage}{\textwidth}
\begin{multicols}{3}
\begin{itemize}[label=\textbullet]
\item \textbf{French} [Native]
\item \textbf{English} [Native]
\item \textbf{Spanish} [Native]


\end{itemize}
\end{multicols}
\end{minipage}

\end{document}
